A Tale of Two Dictionary Learning Problems

### 2020-08-07 manuscripts/thesis/discussion.tex
l1

Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact. To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific structured dictionaries and codes (i.e. estimate $C_1$), and reduced by half for those hoping to prove the consistency of any dictionary learning algorithm (i.e. prove convergence to within $\varepsilon(\delta_1,\delta_2)$ given in \eqref{epsdel}). 
%who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models

>>>>

Indeed, theoretical validation makes little practical difference if the methodology is already in widespread use, while practical criteria establishing whether the data models obtained by practitioners are optimal or not would have very high impact. To this end, the work has been laid out for those wanting to derive statistical criteria for inference with respect to more domain-specific parametric dictionaries and codes (i.e. estimate $C_1$), and reduced by half for those hoping to prove the consistency of any dictionary learning algorithm (i.e. prove convergence to within $\varepsilon(\delta_1,\delta_2)$ given in \eqref{epsdel}). 
%who will derive from our deterministic guarantees the statistical criteria for inference in more domain-specific probabilistic models
